\documentclass[12pt]{beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usetheme{default}
\usepackage{listings}
\newcommand{\li}[1]{\texttt{#1}}
\begin{document}

	\author{Bo Cao}
	\title{Final Presentation of CAS/CSE741}
	\subtitle{Document Polishment, Source Code, Unit VnV, etc.}
	\logo{}
	%\institute{}
	\date{Dec 2, 2019}
	%\subject{}
	%\setbeamercovered{transparent}
	%\setbeamertemplate{navigation symbols}{}
	
	\begin{frame}[plain]
	\maketitle
	\end{frame}

	\section{Document Improvement}
	
	\begin{frame}
		\frametitle{Thanks!}
		Thank you all for your advice!
	\end{frame}
	\begin{frame}
		\frametitle{Possible directions}
		\begin{itemize}
			\item Change SRS to CA.
			\item Elaborate on some points.
			\item Remove MATLAB pseudo-oracle: Small size test cases, manual computation of oracle.
		\end{itemize}
	\end{frame}

	\section{Source Code}
	\subsection{Overview}
	\begin{frame}
		\frametitle{Source Code: Overview}
		Implementing language: C++
		\begin{itemize}
			\item Low-level enough.
			\item Complex grammar and/or supporting libraries.
			\item Template support.
		\end{itemize}
		Future developments: C API
		\begin{itemize}
			\item Some people still use C.
			\item Compatibility.
			\item Easy to build C API based on C++ code.
		\end{itemize}
	\end{frame}

	\subsection{Organize overview}
	\begin{frame}
		\frametitle{Organize}
		Templated class/function.
		\begin{itemize}
			\item Source code distribution
			\item Header file
		\end{itemize}
	\end{frame}

	\subsection{License}
	\begin{frame}
		\frametitle{License}
		MIT License
		\begin{itemize}
			\item Low-level library, source code distribution.
			\item High possibility of commercial usage.
			\item Public, basic knowledge, no potential of revenue.
		\end{itemize}
		Made public for everyone.
	\end{frame}
	
	\subsection{Structure}
	\begin{frame}
		\frametitle{Structure Overview}
		Tree structure from the root header.
		\begin{itemize}
			\item[Leaf] Implement code (data structure/function).
			\item[Non-leaf] Include leaf headers.
		\end{itemize}
		All data structure/function in namespace \li{CFS}
	\end{frame}

	\begin{frame}
		\frametitle{Headers}
		Library all-inclusive header \li{CFS.hpp}
		\begin{itemize}
			\item[Data] \li{CFSData.hpp}
			\item[Behavior Modules]\li{CFSModuleName.hpp}
			\begin{itemize}
				\item[Function] \li{Function.hpp}
			\end{itemize}
		\end{itemize}
	\end{frame}

	\begin{frame}
		\frametitle{Function header template}
		\lstinputlisting[language=c++, linerange=11-24]{../../src/Template.hpp}
	\end{frame}
	\section{Unit VnV}
	\subsection{Overview}
	\begin{frame}
		\frametitle{Tool Introduction}
		\begin{itemize}
			\item Unit Test: Catch2, single header tool
			\item Code Coverage: gcc+gcov
		\end{itemize}
	\end{frame}
	\begin{frame}
		\frametitle{Unit Test structure}
		Controller
		
		TestCase groups
		\begin{itemize}
			\item Test Cases
			\begin{itemize}
				\item Initalize Data
				\item Function Call
				\item Assertion
			\end{itemize}
		\end{itemize}
	\end{frame}
	\subsection{Derivation}
	\begin{frame}
		\frametitle{Test Case Derivation: Data structure and setter/getter}
		\begin{itemize}
			\item Setter/getter pairs: call setter, call getter, compare getter result with setter input.
			\item Exception: Pass data with expected exceptions, check whether excepted exception thrown.
			\item Pairs with index:
			\begin{itemize}
				\item OOR(Out-of-range) exception check: call setter/getter with index overflow/underflow, check exception thrown.
				\item Setter/getter independence: call getter with index $M$, call setter with index $N$($M\neq N$), call getter with index $M$, check whether getter result changed.
			\end{itemize}
		\end{itemize}
	\end{frame}
	\begin{frame}
		\frametitle{Test Case Derivation: Functions}
		\begin{itemize}
			\item Check \li{ToleratedEquality} and dependency first, used for comparison later.
			\item Check other function. If function \li{A} relies on function \li{B}, Check \li{B} before \li{A}.
			\item For each function:
			\begin{itemize}
				\item Check result, if \li{FLOAT/CSFT} type, report error and whether it is within the pre-set tolerance.
				\item Check exceptions thrown if given input with expected exceptions.
			\end{itemize}
		\end{itemize}
	\end{frame}
\end{document}